---
title: "bs {Repbio}"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bs {Repbio}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# bs

## Description

The function `bs` generates a matrix that resamples length with replacement.
The original data set is stored in the first row, while the resamples are stored in the $i_{th}$ row $B_{i}+1$, where $B$ is the total number of resamples.

It returns a matrix *mb* that includes both the original data set and the $i_{th}$ generated resamples.


The seed value is a pseudorandom number, it is an integer value defined by the user. The same results will be returned each time the same number is used, for example: `seed <- 100`; if `seed <- NULL`, different results will be returned each time. For more information, see the set.seed() documentation from the simEd package.


The function requires defining:


 * **df**: A data frame array. 
 * **B**: An integer value, specify the number of resamples.
 * **n**: An integer value indicating the number of observations.
 * **semilla**: An integer value is a seed to initialize a pseudorandom number.


Seealso: `set.seed` from the package simEd (2.0.1)


## bs

The function is included in the `Repbio` package **Reproductive biology analysis**.


```{r setup}
#library(Repbio)
```


The function is detailed below.

```{r, warning=FALSE, message=FALSE}
bs <- function(df,B,n,semilla) {
  set.seed(semilla)
    mb <- matrix(sample(df, size = B * n,
                      replace = TRUE), B, n)
    mb <- rbind(df,mb)  # The resampling data is added with the original data
}     # End function bs
```


## Examples

Falta detallar el ejemplo

```{r, warning=FALSE, message=FALSE}
#       df = tmp
#       B <- 2000
#       n <- 3000
#       semilla <- 100
# # Reproducing the same output every time
#       ejemplo <- bs(df,B,n,semilla)
# 
# # Reproducing the different output every time
#       semilla <- NULL
#       ejemplo <- bs(df,B,n,semilla)
```


## References

Salas‐Singh, C., Morales‐Bojórquez, E., & Aguirre‐Villaseñor, H. (2022). Reproductive biology of the bullseye puffer *Sphoeroides annulatus*: Gonadosomatic index and its suitability for estimating length at maturity. Journal of Fish Biology, 101(5), 1119-1133.https://doi.org/10.1111/jfb.15174
