---
title: "fn_Barplot {Repbio}"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fn_Barplot {Repbio}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# fn_Barplot

## Description

A very simple barplot is generated with no labels or marks for the X-axis,
which serves as the basis for those that will be generated through the
analysis, whether they are simple or compound figures.

It returns a simple barplot that can be upgraded according to needs.

The function requires defining:

 * **df**: A list of matrices with frequencies values.
 * **i**: A numeric value of the ith object in the list.
 * **densidad**: a vector that specifies the shading lines density (in lines
per inch). By default, it is NULL, which means no shading lines. For
more details, see the help of the barplot() function.
 * **angulo**: a vector that specifies the slope of shading lines. For
more details, see the help of the barplot() function

See also: `barplot` from the package graphics (version 3.6.2)


## fn_Barplot

The function is included in the `Repbio` package **Reproductive biology analysis**.


```{r setup}
#library(Repbio)
```


The function is detailed below.

```{r, warning=FALSE, message=FALSE}
fn_Barplot <- function(df,i,densidad,angulo){
  barplot(df[[i]],
          xlab="",
          xaxt = "n",
          legend = FALSE,
          density= densidad,
          angle=angulo,
          border="black",
          col="black"
  )
} # End function
```


## Examples

Falta detallar el ejemplo For example, for two sampled years i = 2 and six factor levels in the
 analyzed variable.

```{r, warning=FALSE, message=FALSE, results='asis'}
      # df <- tmp
      # i <- 2
      # densidad <- c(10,10,30,30,30,10)
      # angulo <- c(3,30,60,90,120,150)
      # 
      # fn_Barplot(df,i,density,angle)
```


## References

Salas‐Singh, C., Morales‐Bojórquez, E., & Aguirre‐Villaseñor, H. (2022). Reproductive biology of the bullseye puffer *Sphoeroides annulatus*: Gonadosomatic index and its suitability for estimating length at maturity. Journal of Fish Biology, 101(5), 1119-1133.https://doi.org/10.1111/jfb.15174
