---
title: "fn_Idioma {Repbio}"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fn_Idioma {Repbio}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# fn_Idioma

## Description

The figure labels are defined as either English (1) or Spanish (2).

It returns the vector **etiquetas**, it is defined by its labels, which include:
total length, frequency, year, month, Gonadosomatic Index, maturity phase,
and residuals. If more tags are needed, it must be redefined.
They should be changed here in the function.


The function requires defining:

 * **idioma**: An integer value that defines the language of the labels. 
 * **language**: A list containing the labels of each language.

## fn_Idioma

The function is included in the `Repbio` package **Reproductive biology analysis**.


```{r setup}
#library(Repbio)
```


The function is detailed below.

```{r, warning=FALSE, message=FALSE}
fn_Idioma <- function(idioma,language){
    if(idioma==1){
        etiqueta<- unlist(language[[1]], use.names = FALSE)
    }else{
        etiqueta<- unlist(language[[2]], use.names = FALSE)
    } # End if
  etiqueta
} # End fn_Idioma
```


## Examples

Falta detallar el ejemplo.

```{r, warning=FALSE, message=FALSE, results='asis'}
  # Labels are in English
  #   idioma <-   1
  #       fn_Idioma(idioma,language)
  # Labels are in Spanish
  #   idioma <-   2
  #       fn_Idioma(idioma,language)
```


## References

Salas‐Singh, C., Morales‐Bojórquez, E., & Aguirre‐Villaseñor, H. (2022). Reproductive biology of the bullseye puffer *Sphoeroides annulatus*: Gonadosomatic index and its suitability for estimating length at maturity. Journal of Fish Biology, 101(5), 1119-1133.https://doi.org/10.1111/jfb.15174
