---
title: "fn_LTGSI {Repbio}"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fn_LTGSI {Repbio}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# fn_LTGSI

## Description

The scattering plot is generated without any labels or marks for the X-axis, 
which is very simple. A horizontal line is included with the threshold value, 
which serves as the basis for the figures that will be generated through the 
analysis, whether they are simple or compound figures.

A scatter plot of the y value by factor level across the x range also includes
a horizontal dashed line representing the threshold value.

Colors are manipulated with the rgb() function of the grDevices package


The function requires defining:


 * **x**: A vector containing the values of the independent variable.. 
 * **y**: A vector containing the values of the dependent variable.. 
 * **df**: A data frame. 
 * **xl**: A label for the X-axis. 
 * **yl**: A label for the y-axis. 
 * **Icut**: A threshold Value. 
 * **ylimit**: A vector value with a minimum and maximum limit for y-axis. 


See also: rgb() from grDevices (version 3.6.2)


## fn_LTGSI

The function is included in the `Repbio` package **Reproductive biology analysis**.


```{r setup}
#library(Repbio)
```


The function is detailed below.

```{r, warning=FALSE, message=FALSE}
fn_LTGSI <- function(x, y, df, xl, yl, Icut, ylimit){
  plot(x , y,
       col = rgb(0,0,0,1/4),
       xlab= xl,
       ylab= yl,
       pch= c(0,1,15,16,17,2)[as.numeric(df$Phase)],
       ylim= ylimit,
       xaxt="n"
      )

      abline(h= Icut,col="black",lty = 2)
}  # End function fn_LTGSI
```


## Examples

Falta detallar el ejemplo.

```{r, warning=FALSE, message=FALSE, results='asis'}
 #  x <-x
 #  y <- y
 #  df <- tmp
 #  xl <- etiquetas[1]
 #  yl <- etiquetas[3]
 #  Icut <- 2.3
 #  ylimit <- c(0,45)
 # ejemplo <- fn_LTGSI(x, y, df, xl, yl, Icut, ylimit)
```


## References

Salas‐Singh, C., Morales‐Bojórquez, E., & Aguirre‐Villaseñor, H. (2022). Reproductive biology of the bullseye puffer *Sphoeroides annulatus*: Gonadosomatic index and its suitability for estimating length at maturity. Journal of Fish Biology, 101(5), 1119-1133.https://doi.org/10.1111/jfb.15174
