---
title: "modelo {Repbio} "
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{modelo {Repbio}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# modelo

## Description

Fit the model using the nlsLM function. For more details see the function
documentation: nlsLM() from minpack.lm (version 1.2-4).

Arguments are 'genero' (Gender),'idioma' (Lenguage) and Phases (maturity phases)
 * genero: Value *1* selects Females and *2* Males
 * idioma: Value *1* selects English language and *2* Spanish language
 * Phases: Value *1* selects the roman numeral and *2* phases name


The function requires defining:

 * **x**: independent variable.
 * **y**: dependent variable.
 * **mod**: A nonlinear model formula including variables and parameters. Will
be coerced to a formula if necessary.
 * **bb**: A list or numeric vector of starting estimates. If par is a
list, then each element must be of length 1.
 * **bmin**: A numeric vector of lower bounds on each parameter. If not
given, the default lower bound for each parameter is set to -Inf.
 * **bmax**: A numeric vector of upper bounds on each parameter. If not
given, the default upper bound for each parameter is set to Inf.

See also: `nlsLM` from minpack.lm (version 1.2-4).


## modelo

The function is included in the `Repbio` package **Reproductive biology analysis**.


```{r setup}
#library(Repbio)
```


The function is detailed below.

```{r, warning=FALSE, message=FALSE}
modelo <- function(x,y,mod,bb,bmin,bmax){
  nlsLM(formula = mod,
        start = bb,
        lower = bmin,
        upper = bmax
  )
} # End function
```


## Examples

Falta detallar el ejemplo

```{r, warning=FALSE, message=FALSE, results='asis'}
    # modelo(x,y,mod,bb,bmin,bmax)
```


## References

Salas‐Singh, C., Morales‐Bojórquez, E., & Aguirre‐Villaseñor, H. (2022). Reproductive biology of the bullseye puffer *Sphoeroides annulatus*: Gonadosomatic index and its suitability for estimating length at maturity. Journal of Fish Biology, 101(5), 1119-1133.https://doi.org/10.1111/jfb.15174
