---
title: "strb {Repbio}"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{strb {Repbio}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# strb

## Description

This function helps in the visual search of the starting input parameters
for nlsLM, to fit the specified model (mod), using a graph for visual
adjustment of model parameters (Trial and Error Strategy).

It returns: a plot with the observed, fitted values and its confidence interval,
and a model settings list.

The function requires defining:


 * **b3**: The initial value for the medium asymptote. Valid only for double
sigmoid model, NA is assigned for the simple model.
 * **b4**: The initial value for the coordinate at the inflection point for
simple sigmoid model. For the double sigmoid model, it corresponds
to the first inflection point.
 * **b5**: The initial value for the amplitudes of the sigmoid, for the double
sigmoid model corresponds to the amplitude of the first sigmoid.
b5= L95a-b4 ,L95a is the lengths at 95 percent maturity for the
complete sigmoid (single model) or the first sigmoid (double model).
 * **b6**: The coordinate at the second inflection point. Valid only for double
sigmoid model, NA is assigned for the simple model.
 * **b7**: The initial value for the amplitude of the second sigmoid. Valid
only for double sigmoid model, NA is assigned for the simple model.
b7= L95b-b6 ,L95b is the lengths at 95 percent maturity from the
second distribution.
 * **x**: independent variable.
 * **y**: dependent variable.
 * **mod**: A nonlinear model formula including variables and parameters.
 * **modelo**: function from Repbio, to fit the specified model (mod).
 * **bl**: Lower (bl) weight values apply to each parameter (bi).
 * **bu**: Upper (bu) weight values apply to each parameter (bi)
 * **xl**: Title label for X axis.
 * **yl**: Title label for Y axis.

See also: `nlsLM` from minpack.lm (version 1.2-4).


## strb

The function is included in the `Repbio` package **Reproductive biology analysis**.


```{r setup}
#library(Repbio)
```


The function is detailed below.

```{r, warning=FALSE, message=FALSE}
strb <- function(b3,b4,b5,b6,b7,x,y,mod,modelo, bl, bu, xl, yl){
  bb <- c(b3=b3,b4=b4,b5=b5,b6=b6,b7=b7)
  bb <- bb[!is.na(bb)]
  bmin <- c(bb*bl)
  bmax <- c(bb*bu)
  fit <- modelo(x,y,mod,bb,bmin,bmax)

  plot(x,y,
       xlab=xl,
       ylab= yl)
  lines(x,fitted(fit))

  fit
} # End function
```


## Examples

Falta detallar el ejemplo

```{r, warning=FALSE, message=FALSE, results='asis'}
    # strb(b3,b4,b5,b6,b7,x,y,mod,modelo, bl, bu, xl, yl)
```


## References

Salas‐Singh, C., Morales‐Bojórquez, E., & Aguirre‐Villaseñor, H. (2022). Reproductive biology of the bullseye puffer *Sphoeroides annulatus*: Gonadosomatic index and its suitability for estimating length at maturity. Journal of Fish Biology, 101(5), 1119-1133.https://doi.org/10.1111/jfb.15174
